\documentclass[overlapped,line,letterpaper, 12pt]{res}

\usepackage{ifpdf}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Baishakhi Ray},
  pdfcreator={$ $Id: cv-bray.tex,v 1.0 10/21/2013 13:59:29 baishakhi Exp $ $},
  pdfsubject={Curriculum Vitae},
}

	
\def\labelitemi{--}

%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

% Make a nicer C++
\def\Cplusplus{C{\raise.5ex\hbox{\footnotesize ++ }}}

%---------------------------------------------------------------------------

\name{Baishakhi Ray}

\begin{resume}

\begin{ncolumn}{2}

%Electrical \& Computer Engineering  & Phone: (303) 748-2958 \\
%The University of Texas at Austin     & {Email: \tt rayb@utexas.edu} \\
%Austin,  Tx - 78712                         & {http://rayb.info} \\

Postdoctoral Researcher                    & \\
Department of Computer Science      & Phone: (303) 748-2958 \\
University of California Davis              & {Email: \tt bairay@ucdavis.edu} \\
Davis,  CA - 95616                            & {http://rayb.info} \\

\end{ncolumn}

%---------------------------------------------------------------------------
%\section{\bf Target Position} Research internship for summer 2013.
%\section{\bf Objective} Looking for a postdoc position to do exciting and influential research in software engineering and related areas.
% in a research lab for software engineering related research. 

\section{\bf Research Interest}
%Program Analysis (automatic error/bug detection, fault localization), 
%Empirical Software Engineering (big data analysis, defect prediction ),
%Software Engineering (software metric, software quality, bug analysis),
%Open Source Software Development,
%Mobile Computing
I am primarily interested in Software Engineering, in particular, analyzing large scale software to understand current software engineering practices. Based on this understanding, I develop novel program analysis techniques to make software more reliable and secure.

\section{\bf Education}

{\bf Ph.~D., Electrical \& Computer Engineering, University of Texas, Austin}. \\
  August 2013  (GPA: 3.97)\\
Thesis: Analysis of Cross-System Porting and Porting Errors in Software Projects \\
Advisor: Prof. Miryung Kim 

{\bf MS, Computer Science, University of Colorado, Boulder}. \\ 
May 2009 (GPA: 4.0) \\
Thesis: SecureWear: Securing Wearable Mobile Social Networks \\
Advisor: Prof. Richard Han

%\begin{itemize}
%\item { Courses: Operating Systems, Computer Architecture,
%				 Network Security, Distributed Systems, Graduate Algorithms
%}	
%\item {GPA: 4.0}
%\item {Thesis topic: SecureWear: Securing Wearable Mobile Social Networks}

%\end{itemize}

{\bf B.Tech. \& B.Sc., Computer Science \& Physics, Calcutta University}, \\ 2004 
% Computer Science \& Engineering , Physics \\
(GPA: 3.84, Top 1\% in University)

%\begin{itemize}
%\item {Major: Computer Science \& Engineering , Physics}
%\item {GPA: 3.84, Top 1\% in University}
%\item {Selected for summer scholarship in Jawaharlal Nehru Scholarship for Advanced
%Research (only 100 students are selected Nationwide)}
%\end{itemize}
%---------------------------------------------------------------------------



%%===========================================================================%%
%\newpage
%\opening
\section{\bf Honors}

\begin{itemize}
\item[--]
Best Practical Paper Award, IEEE Symposium on Security and Privacy 2014
\item[--]
Google Summer of Code 2012\\ (mentors: Dr.~Suzette Person \& Dr.~Neha Rungta, NASA)
\item[--]
SIGSOFT FSE 2012 CAPS travel award 
\item[--]
Jawaharlal Nehru Summer Scholarship for Advanced Research, India 2001.
 % (only 100 students are selected Nationwide).
\end{itemize}

\section{Selected Publications}
\vspace{-0.1cm}
\section{\small Full Length Research Papers}

\begin{itemize}
\item[--]
{\em Using Frankencerts for Automated Adversarial Testing of Certificate Validation in SSL/TLS Implementations}. 
C.~Brubaker, S.~Jana, {\bf B.~Ray}, S.~Khurshid, and V.~Shmatikov \\
%Chad Brubaker, Suman Jana, {\bf Baishakhi Ray}, Sarfraz Khurshid, and Vitaly Shmatikov \\
{\small In 35$^{th}$ IEEE Symposium on Security and Privacy, MAY, 2014 (S\&P (Oakland) '14).}\\
\textbf{\small Best Practical Paper Award}


\item[--]
{\em Detecting and Characterizing Semantic Inconsistencies in Ported Code}. 
%{\bf Baishakhi Ray}, Miryung Kim, Suzette Person, Neha Rungta.\\
{\bf B.~Ray}, M.~Kim, S.~Person, N.~Rungta.
{\small In 28$^{th}$ IEEE/ACM International Conference on Automated Software Engineering, 
November, 2013 (ASE'13).}
\textbf{\small Nominated for Distinguished Paper award.}


\item[--]
{\em An Empirical Study of API Stability and Adoption in the Android Ecosystem}. 
%Tyler McDonnell, {\bf Baishakhi Ray},  Miryung Kim.
T.~McDonnell, {\bf B.~Ray},  M.~Kim. 
{\small In 29$^{th}$ IEEE International Conference on Software Maintenance, April, 2013 (ICSM'13).}

\item[--]
{\em A Case Study of Cross-System Porting in Forked Projects}. 
%{\bf Baishakhi Ray}, Miryung Kim. \\
{\bf B.~Ray}, M.~Kim.
{\small In ACM SIGSOFT, the 20$^{th}$ International Symposium on the Foundations of Software Engineering
(FSE'12).}

\item[--]
{\em An Empirical Study of Supplementary Bug Fixes}. 
%Jihun Park, Miryung Kim, {\bf Baishakhi Ray}, DooHwan Bae. \\
J.~Park, M.~Kim, {\bf B.~Ray}, D.~Bae. 
{\small In The 9$^{th}$ IEEE Working Conference on Mining Software Repositories (MSR'12).}
\textbf{\small{Invited to the Special Issue of Journal of Empirical Software Engineering (EMSE)}}.

\item[--]
{\em PTask: Operating System Abstractions To Manage GPUs as Compute Devices}.
CJ.~Rossbach, J.~Currey, M.~Silberstein, {\bf B.~Ray}, E.~Witchel. 
{\small In Proceedings of the 23$^{rd}$ ACM Symposium on Operating System Principles (SOSP'11)}. 

%\item[--]
%{\bf Baishakhi Ray}, S. Ananthanarayan, S. Mishra. \\
%{\em A Reliable Transmission Protocol for Sensors in Poorly Connected Areas over Mobile Networks}. 
%In International Conference on Parallel and Distributed computing and Networks (PDCN'10).

\item[--]
{\em A Protocol for Building Secure and Reliable Covert Channel}. 
{\bf B.~Ray} and S.~Mishra. \\
{\small In 6$^{th}$ Annual Conference on Privacy, Security and Trust, 2008. (PST'08).}

\item[--]
{\em WhozThat?: Evolving an Ecosystem for Context-Aware Mobile Social Networks}.
A. Beach, {\bf B.~Ray}, et al., {\small In IEEE Network Magazine Special Issue on Composable context aware services, 
2008.}

\item[--]
{\em SecureWear: A Framework for Securing Mobile Social Networks}.
%{\bf Baishakhi Ray},  Richard Han. 
{\bf B.~Ray},  R.~Han. 
{\small In Advances in Computer Science and Information Technology. Computer Science and Engineering, Lecture Notes of the Institute for Computer Sciences, Social Informatics and Telecommunications Engineering, 2012.}
%(LNJCST Series), 2012.
%, Springer, Volume 85, Part 1, pp. 515-524, DOI: 10.1007/978-3-642-27308-7_55, (from The Second International Conference on Computer Science and Information Technology (CCSIT)).
%\end{enumerate}
\end{itemize}

\section{\small Under Submission}

\begin{itemize}
\item[--]
%{\bf Baishakhi Ray} , Daryl Posnett , Vladimir Filkov, Premkumar T Devanbu \\
{\em A Large Scale Study of Programming Languages and Code Quality in Github}. 
{\bf B.~Ray} , D.~Posnett , V.~Filkov, P.~T.~Devanbu 


\item[--]
%{\bf Baishakhi Ray}, Meiyappan Nagappan, Christian Bird, Nachiappan Nagappan, Thomas Zimmermann.\\
{\em The Uniqueness of Changes: Characteristics and Applications}. 
{\bf B.~Ray}, M.~Nagappan, C.~Bird, N.~Nagappan, T.~Zimmermann.

\end{itemize}

\section{\small Short Papers}

\begin{itemize}
\item[--]
%{\bf Baishakhi Ray}, Christopher Wiley, Miryung Kim.\\
{\em Repertoire: A Cross-System Porting Analysis Tool for Forked Software Projects}. 
{\bf B.~Ray}, C.~Wiley, M.~Kim.
{\small In ACM SIGSOFT the 20$^{th}$ International Symposium on the Foundations of Software Engineering, Formal Research Tool Demonstration (FSE'12).}

\item[--]
{\em Touch Me wE@r: Getting Physical with Social Networks},
A. Beach, {\bf Baishakhi Ray}, L. Buechley. 
{\small In 2009 Workshop on Sensor-based Models and Feedback Systems for Social Computing. associated with SocialCom 2009.}
\end{itemize}

\section{\bf Teaching Experience}
\vspace{1cm}
\begin{itemize}
\item
{\bf Mentoring}: Tyler McDonnell, Connie Nguyen
\item
%{\bf Guest Lecturer}: Software Engineering (Fall'13), UC Davis.
%\item
{\bf Guest Lecturer}: Software Engineering and Design Laboratory (Fall'13), UT Austin
                                 Software Engineering (Fall'13), UC Davis.
\item 
{\bf Teaching Assistant}: Mobile Computing (Fall'10), UT Austin.
\item
{\bf Grader}: Operating Systems (Spring'08), Networking (Fall'08), UC Boulder.
\end{itemize}

\section{\bf Research Internship}
\begin{format}
\employer{l}
%\title{l}\\
\dates{r} \\
\body\\
\end{format}
\vspace{0.5cm}

\employer{{\bf Microsoft Research, Redmond, USA}}
\dates{May 2013--August 2013}
\begin{position}
Mentors: Christian Bird, Nachiappan Nagappan, Thomas Zimmermann \\
We studied how uniquely developers change code by statically analyzing source code of two large Microsoft projects.
Leveraging this understanding, we implemented a change recommendation system and a bug prediction tool.
Findings of this work is currently under submission.
\end{position}

%\vspace{-1cm}

%\title{{\it Summer Intern}}
\employer{{\bf Google Summer Code, Google Inc.}}
\dates{{\it May 2012 -- August 2012}}
\begin{position}
Mentors: Suzette Person, Neha Rungta, NASA \\
We implemented a tool, called SPA, that automatically detects and characterizes porting errors that developers often 
introduce while copying code from one place to another. Findings of this research is published in ASE 2013.
\end{position} 

%\vspace{-1cm}


\section{\bf Professional Experience}

%\begin{format}
%\title{l}\dates{r}\\
%\employer{l}\location{r}\\
%\body\\
%\end{format}

\begin{format}
\employer{l}\\
\title{l}\dates{r} \\
\body\\
\end{format}
\vspace{0.5cm}
\employer{{University of California Davis},  CA, USA}
\title{{Postdoctoral Research Fellow}}
\dates{{October 2013 - present}}
\begin{position}
\end{position} 

\vspace{-1cm}


\title{{Research Assistant}}
\employer{{The University of Texas at Austin}, TX, USA}
\dates{{January 2011--May 2013}}
\begin{position}
\end{position}

\vspace{-1cm}



\title{{Software Engineer}}
\employer{{Ericsson Pvt. Ltd.}, Boulder, CO, USA}
\dates{{Feb 2009--June 2010}}
\begin{position}
%Developed SCTP (Stream Control Transmission Protocol) stack.
\end{position}

\vspace{-1cm}

\title{{Summer Intern}} %Research Internship, Avaya, CO}
\employer{{Avaya Research Lab}, Westminster, CO, USA}
%\location{Westminster, CO}
\dates{{May 2008 -- Aug 2008}}
\begin{position}
%Designed and implemented a mobile application to periodically send location information during a SIP call in S60 platform.  
\end{position}

\vspace{-1cm}

\title{{Software Engineer}}%, Ixia Communication}
\employer{{Ixia Technologies Pvt. Ltd.}, India}
%\location{India}
\dates{{Oct 2005--July 2007}}
\begin{position}
%Designed and developed a virtual Network Interface Card driver in Windows.
%(with WinDDK, NDIS Miniport Driver) and various User-mode protocol stacks.
\end{position}

\vspace{-1cm}

\title{{Software Engineer}}%, Texas Instruments} %\& Sasken Communication Technology, India}
\employer{{Texas Instruments} \& {Sasken}, India}
%\location{India}
\dates{{Aug 2004 -- Oct 2005}}
\begin{position}
%Implemented camera device and image processing unit on a GSM-only ARM7 platform.
\end{position}

\section{\bf Professional Services}

\begin{itemize}
\item
Program Committee: {\small FSE  Artifact '14, ISEC '14, OOPSLA Artifact '13}
\item
Reviewer: {\small Transactions on Software Engineering (TSE), CSI Journal Computer Standards \& Interfaces}
\item
External Reviewer: {\small ASE '14,  MSR '12, OOPSLA '12}
\item
{\small Vice President, Graduate Women in Engineering, ECE Department,  UT Austin}
\end{itemize}

\section{\bf References}

\begin{itemize}
\item
Prof.~Miryung Kim,  {\tt miryung@ece.utexas.edu}
\item
Prof.~Premkumar T.~Devanbu, {\tt devanbu@cs.ucdavis.edu}
\item
Prof.~Sarfraz Khurshid, {\tt khurshid@ece.utexas.edu}
\item 
Dr. Thomas Zimmermann, {\tt tzimmer@microsoft.com}

\end{itemize}

%%---------------------------------------------------------------------------%%
%\section{\bf Technical Skills}
%\begin{itemize}
%\item {\bf Programming:} C/C++, Java, Assembly Languages, Unix shell scripting, Python.
%\item {\bf OS:} Linux, Windows XP/2000/Vista
%\item {\bf Development Tools/Techniques:}
%\begin{enumerate}
%\item Java Path Finder, Control-Data flow analysis, LLVM, CCFinder, gdb, Makefile
%\item Control systems (Clearcase, SVN, CVS, perforce) 
%\item gdb, Makefile
%%\item Knowledge of configuration of different networking equipments 
%
%%\item Wireless device drivers (Madwifi, intel 3945 )
%\item Linux kernel programming
%\end{enumerate}
%\end{itemize}


\end{resume}

\end{document}

%%===========================================================================%%
